Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-25 robdml.tex
tex

\section{Discussions}
\label{sec:5}

(optional) ICS for ACT?

\section{Conclusion}
\label{sec:6}

HM follows the min-max paradigm, (can be incorporated into FAT etc).
Both ACT and HM stops at a specific point.

>>>>

\section{Conclusion}
\label{sec:5}

Adversarial robustness is important for DML applications, but
the existing defenses still suffer from low efficiency and low
performance.
%
In this paper, 
Hardness Manipulation is proposed as as a flexible tool to create
adversarial examples for more efficient adversarial training.
%
Meanwhile, Gradual Adversary is proposed as a family of pseudo-hardness
functions to better balance the training objectives.
%
Besides, an Intra-Class Structure penalty is proposed to enforce better
embedding structure for higher robustness.
%
According to experimental evaluations, the proposed method overwhelmingly
outperforms the state-of-the-art defenses.
